DRAFT: Social Learning and Shared Belief: The Importance of Bias and Trust for Information Diffusion

### 2014-08-22 paper/paper.tex
add truth

>>>>

Using the graph of newspapers and periods we are able to build a measure of the likelihood of each topic for each period.  Naively this could be done by treating each newspaper as an observation and determing the proportion of each topic in each period.  Unfortunately, this ignores one possible concern which is that each newspaper is unlikely to be indpendent.  As a result we use an alternative measure as well.  Our measure is the probability that the observations we are making are independent of influence of other newspapers.  We calculate this measure by getting the probability that each observation is independent,

\[P(TI_{it+1}) = \prod_{j=1}^J (1 - P(T_{it+1} | T_{jt}))P(T_{it+1})\]

where J is the number of newspapers that reported on a topic in the previous period.  We use both this measure and the naive measure later in the paper.
